A free/open-source Kazakh-Tatar machine translation system

### 2013-04-22 paper/paper.tex
a space fix

The bilingual lexicon currently contains 9,269 stem-to-stem correspondences and was built mostly 
by hand (i.e., by translating Kazakh stems unrecognised by the morphological analyser into Tatar).  Some 
toponyms and other proper names were translated semi-automatically by looking up links in Wikipedia \citep{tyers08}; also, 
some Russian loanwords common to both languages (such as автомобиль, гонорар, etc.) were added to the bilingual 
dictionary automatically by taking the intersection of Russian and Kazakh wordlists.

>>>>

The bilingual lexicon currently contains 9,269 stem-to-stem correspondences and was built mostly 
by hand (i.e., by translating Kazakh stems unrecognised by the morphological analyser into Tatar).  Some 
toponyms and other proper names were translated semi-automatically by looking up links in Wikipedia \citep{tyers08}; also, 
some Russian loanwords common to both languages (such as автомобиль, гонорар, etc.)\ were added to the bilingual 
dictionary automatically by taking the intersection of Russian and Kazakh wordlists.
